Supplementary Information

### 2025-05-11 Paper/Source/supp.tex
finalize first draft

\subsection*{Siqi Pan and Shuguang Zhang}

\begin{figure}[H]
    \caption{\textbf{The enlarge protein sequence alignments of 12 retinylidene proteins with their water-soluble QTY analogs from Figure 1.} The symbols $|$ and $*$ indicate that amino acids are identical and different respectively. Amino acids L, V, I and F in TM (transmembrane) alpha helices are replaced with Q, T, Y and Y respectively. The alpha helices (blue) are shown above the protein sequences. \\
    The alignments are: 
    \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
    \textbf{b)} OPN1LW \textit{vs} OPN1LW$^{\textrm{QTY}}$, 
    \textbf{c)} OPN1SW \textit{vs} OPN1SW$^{\textrm{QTY}}$, 
    \textbf{d)} OPN2 \textit{vs} OPN2$^{\textrm{QTY}}$, 
    \textbf{e)} OPN3 \textit{vs} OPN3$^{\textrm{QTY}}$, 
    \textbf{f)} OPN4 \textit{vs} OPN4$^{\textrm{QTY}}$, 
    \textbf{g)} OPN5 \textit{vs} OPN5$^{\textrm{QTY}}$, 
    \textbf{h)} RGR \textit{vs} RGR$^{\textrm{QTY}}$, 
    \textbf{i)} RRH \textit{vs} RRH$^{\textrm{QTY}}$, 
    \textbf{j)} BACR \textit{vs} BACR$^{\textrm{QTY}}$, 
    \textbf{k)} BACH \textit{vs} BACH$^{\textrm{QTY}}$, 
    \textbf{l)} ChR2 \textit{vs} ChR2$^{\textrm{QTY}}$. }
    \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn1mw.jpg}
\end{figure}

@@

\newpage
\begin{figure}[H]
    \textbf{j)} BACR$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 bacr qty mono.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{k)} BACH$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 bach qty mono.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{l)} ChR2$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 chr2 qty mono.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{m)} BACR$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 bacr qty tri.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{n)} BACH$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 bach qty tri.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{o)} ChR2$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 chr2 qty di.jpg}
\end{figure}

>>>>

\subsection*{Siqi Pan}

\begin{figure}[H]
    \caption{\textbf{The enlarged protein sequence alignments of 12 retinylidene proteins and their QTY analogs from Figure 1. } The symbols $|$ and $*$ indicate that amino acids are identical or different, respectively. Amino acids L, I/V, and F in TM (transmembrane) alpha helices (shown in blue above the sequences) are replaced with Q, T, and Y respectively. The variation in the TM domain ranges from 35.53\% to 50.24\% while the overall variation rate ranges from 15.48\% to 30.04\%. 
    The alignments are 
    \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
    \textbf{b)} OPN1LW \textit{vs} OPN1LW$^{\textrm{QTY}}$, 
    \textbf{c)} OPN1SW \textit{vs} OPN1SW$^{\textrm{QTY}}$, 
    \textbf{d)} OPN2 \textit{vs} OPN2$^{\textrm{QTY}}$, 
    \textbf{e)} OPN3 \textit{vs} OPN3$^{\textrm{QTY}}$, 
    \textbf{f)} OPN4 \textit{vs} OPN4$^{\textrm{QTY}}$, 
    \textbf{g)} OPN5 \textit{vs} OPN5$^{\textrm{QTY}}$, 
    \textbf{h)} RGR \textit{vs} RGR$^{\textrm{QTY}}$, 
    \textbf{i)} RRH \textit{vs} RRH$^{\textrm{QTY}}$, 
    \textbf{j)} BACR \textit{vs} BACR$^{\textrm{QTY}}$, 
    \textbf{k)} BACH \textit{vs} BACH$^{\textrm{QTY}}$, 
    \textbf{l)} ChR2 \textit{vs} ChR2$^{\textrm{QTY}}$. }
    \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn1mw.jpg}
\end{figure}

@@

\newpage
\begin{figure}[H]
    \textbf{j)} BACR$^{\textrm{QTY}}$ monomer \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 bacr qty mono.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{k)} BACH$^{\textrm{QTY}}$ monomer \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 bach qty mono.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{l)} ChR2$^{\textrm{QTY}}$ monomer \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 chr2 qty mono.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{m)} BACR$^{\textrm{QTY}}$ trimer \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 bacr qty tri.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{n)} BACH$^{\textrm{QTY}}$ trimer \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 bach qty tri.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{o)} ChR2$^{\textrm{QTY}}$ dimer \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 chr2 qty di.jpg}
\end{figure}
